Ecuador plant occurrence data merging

### 2023-02-27 code/L2/L2_Ecuador_plant_occ.Rmd
Add code acknowledgments

# Read in the configuration table
```{r}
metadata <-
  readr::read_csv(file.path(data_path, "occ_metadata.csv"),
                  show_col_types = FALSE)
```

# Read in BIEN, GBIF, and IUCN occurrence data

```{r}
database <-
bdc_standardize_datasets(metadata = metadata,
                         format = "csv",
                         overwrite = TRUE,
                         save_database = FALSE)
```

>>>>

# Read in the configuration table
Using bdc package; modified from https://brunobrr.github.io/bdc/articles/integrate_datasets.html
```{r}
metadata <-
  readr::read_csv(file.path(data_path, "occ_metadata.csv"),
                  show_col_types = FALSE)
```

# Read in BIEN, GBIF, and IUCN occurrence data
Using bdc package; modified from https://brunobrr.github.io/bdc/articles/integrate_datasets.html
```{r}
database <-
bdc_standardize_datasets(metadata = metadata,
                         format = "csv",
                         overwrite = TRUE,
                         save_database = FALSE)
```
